Сравнение подходов к ранжированию

### 2016-01-08 article3.Rmd
Изменен рисунок

```{r sc.time}
agg.doe<-agg.doe[,c(1,2,9:11)]
names(agg.doe)[3:5]<-c("Шульце","Кемени","ЛП")
md<-melt(agg.doe,id=c("val","experts"))
md<-aggregate(value~val+variable,sum,data=md)
ggplot(md,aes(x=val,y=value,col=variable))+
  geom_line(size=1)+geom_point()+
 scale_color_discrete(name="Алгоритм")+
  scale_y_log10(breaks=trans_breaks("log10",function(x) 10^x),
                labels=trans_format("log10",math_format(10^.x)),
                minor_breaks=waiver())+  
  labs(x="Число параметров",y="Время, сек.")+
  theme_bw()+theme(text=element_text(size=14))
ggsave("Pic03_00.png",width=6,height=4,dpi=300)
```

>>>>

```{r sc.time}
agg.doe<-agg.doe[,c(1,2,9:11)]
names(agg.doe)[3:5]<-c("Шульце","Кемени","ЛП")
md<-melt(agg.doe,id=c("val","experts"))
md<-aggregate(value~val+variable,sum,data=md)
ggplot(md,aes(x=val,y=value,linetype=variable))+
  geom_line(size=1)+geom_point()+
 scale_linetype_discrete(name="Алгоритм")+
  scale_y_log10(breaks=trans_breaks("log10",function(x) 10^x),
                labels=trans_format("log10",math_format(10^.x)),
                minor_breaks=waiver())+  
  labs(x="Число параметров",y="Время, сек.")+
  theme_bw()+theme(text=element_text(size=14))
ggsave("Pictures/Artcl03/Pic03_00.png",width=6,height=4,dpi=300)
```
